Integrating Social Visual Analysis and Deployment with RCloud

### 2015-03-27 relatedwork.tex
fig 2
working

There is much previous work that inspired or influenced ours.
Indeed, many studies have addressed the requirements for future visual
analytics environments.
Previous work that we learned from includes:

{\bf Vistrails} as a landmark prototype of a scientific workflow
and provenance management system. This prototype helped the community
to understand the value of capturing aspects of the processes that
surround data analysis experiments and tools, including detailed
history, collaboration, and deployment.

@@

{ManyEyes} is the best-known original work showing the potential for
integrating data visualization with social media.

@@

Kandel et al.'s interview study points out the typical ``explore'',
``model'', ``report'' cycle in enterprise data
analysis~\cite{Kandel:2012:EDA}. There are many discontinuities in
this cycle that cost time and effort to overcome. RCloud seeks to
reduce this mismatch. Kandel et al also point out that larger teams
are becoming more common in data analysis, that supporting
collaboration is difficult and important, and that sharing
and versioning of data sources and artifacts is hindered by current
technology. ``We found that analysts typically did not
share scripts with each other. Scripts that were shared were
disseminated similarly to intermediate data: either through shared
drives or email. Analysts rarely stored their analytic code in source
control.'' Their work points to the opportunity for better technology
to support collaboration and sharing in data analysis teams.

An earlier study by Kandel et al argues that data wrangling
(cleaning, parsing and transformation)is a major part of exploratory
analysis and visualization~\cite{Kandel:2011:RDI}. We view this
as attacking a different semantic level than ours, but points
to the need for an environment that enables better sharing
of the knowledge, tools and processes to do this. Anecdotally
we find much frustration among practitioners that this knowledge
is difficult to find and often not recorded or provided in a reusable
form even within one organization.

@@

Manyeyes \cite{Viegas:2007:MAS} was a landmark system for the integration
of social media with visualization and data publishing. We build on this
work by defining a rich interface for collaboration about code, and for
operating on metadata.

@@

There has been noteworthy work on specific techniques such as
social bookmarking \cite{Millen:2006:DSB} \cite{Heer:2007:VAV}
and crowdsourcing \cite{Fast:2014:ECS} to support collaborative
or social development or analysis processes.
Similarly, there are computational methods to support high
performance execution in incremental code development
environments \cite{Guo:2010:TPI}.
Our present goal is to define an environment in which many such
techniques may be integrated and made available to a broad community.

VisMashup~\cite{Santos:2009:VST} and Crowdlabs~\cite{Mates:2011:CSA}
are tools built on top of the VisTrails workflow management
system~\cite{Callahan:2006:VVM}. VisMashup defines a schema and
semantics for automatically deriving user interfaces from workflows,
while Crowdlabs exposes these capabilities on a website feature
workflow upload and remote execution. In our view, the impedance
mismatch between a dataflow pipeline specification and the power of a
general-purpose language is too great for the type of general
exploratory work in data science teams. As a result, RCloud tries to
provide a closer match for analysts accustomed to creating and
executing R and Python code, while retaining attractive
properties like automatic versioning and management.

@@

One overall goal is to reduce the gap between implementers and deployers
of technology in visual analytics. The fusion of development with production
operations in software release management (``DevOps'' \cite{Httermann:2012:DD}
or ``continuous integration'' \cite{Fowler:2006:Continuous}) is a trend in web
services and related fields.
By making it convenient for data scientists to expend just a little more effort
in the process of creating experiments, we may be able to eliminate the need
for programming teams to recreate their work in production which has a high
penalty in time, expense and sometimes correctness.

>>>>

\stephen{In addition to the immense foundation of work on systems
for statistical computing,}
There is much previous work that inspired or influenced ours.
Indeed, many studies have addressed requirements for future visual
analytics environments.
Previous work that we learned from includes:

{\bf VisTrails} as a landmark prototype of a scientific workflow
and provenance management system. This prototype demonstrated
the value of capturing aspects of the processes that
surround data analysis experiments and tools, including detailed
history, collaboration, and deployment.

@@

@@

Kandel et al.'s interview study points out the typical ``explore'',
``model'', ``report'' cycle in enterprise data
analysis~\cite{Kandel:2012:EDA}. There are many discontinuities in
this cycle that cost time and effort to overcome. RCloud seeks to
reduce this mismatch. Kandel et al also point out that larger teams
are becoming more common in data analysis, that supporting
collaboration is difficult and important, and that sharing
and versioning of data sources and artifacts is hindered by current
technology. ``We found that analysts typically did not
share scripts with each other. Scripts that were shared were
disseminated similarly to intermediate data: either through shared
drives or email. Analysts rarely stored their analytic code in source
control.'' Their study highlights the opportunity for better ways
of supporting collaboration and sharing in data analysis teams.

An earlier study by Kandel et al argues that data wrangling
(cleaning, parsing and transformation)is a major part of exploratory
analysis and visualization~\cite{Kandel:2011:RDI}. We view this
as attacking a different semantic level than ours, but also
showing the need for an environment that enables better sharing
of the knowledge, tools and processes to do this. Anecdotally
we find much frustration among practitioners that this knowledge
is difficult to find and often isnot recorded or available in a
reusable form even within the same organization.

@@

{\bf Manyeyes} \cite{Viegas:2007:MAS} was a landmark system for the integration
of social media with visualization and data publishing. We build on this
work by defining a rich interface for collaboration about code, and for
operating on metadata.

@@

There has been noteworthy work on specific techniques such as
social bookmarking \cite{Millen:2006:DSB} \cite{Heer:2007:VAV}
and crowdsourcing \cite{Fast:2014:ECS} to support collaborative
or social development or analysis processes.
Similarly, there are computational methods to support high
performance execution in incremental code development
environments \cite{Guo:2010:TPI}.
The goal of RCloud is to define an environment in which many such
techniques may be integrated and made available to a broad community.

{\bf VisMashup}~\cite{Santos:2009:VST} and Crowdlabs~\cite{Mates:2011:CSA}
are tools built on top of the VisTrails workflow management
system~\cite{Callahan:2006:VVM}. VisMashup defines a schema and
semantics for automatically deriving user interfaces from workflows,
while Crowdlabs exposes these capabilities on a website feature
workflow upload and remote execution. In our view, the impedance
mismatch between a dataflow pipeline specification and the power of a
general-purpose language is too great for the type of general
exploratory work in data science teams. As a result, RCloud tries to
provide a closer match for analysts accustomed to creating and
executing R and Python code, while retaining attractive
properties like automatic versioning and management.

@@

One overall goal is to reduce the gap between implementers and deployers
of technology in visual analytics. The fusion of development with production
operations in software release management (``DevOps'' \cite{Httermann:2012:DD}
or ``continuous integration'' \cite{Fowler:2006:Continuous}) is a trend in web
services and related fields.
By making it convenient for data scientists to expend just a little more effort
in the process of creating experiments, we may be able to eliminate the need
for programming teams to recreate their work in production, which has a high
penalty in time, expense and accuracy.
